---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metapropul

<!-- badges: start -->
[![R-CMD-check](https://github.com/drrubesh/metapropul/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/drrubesh/metapropul/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/drrubesh/metapropul/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/drrubesh/metapropul/actions/workflows/pkgdown.yaml)
<!-- badges: end -->

`metapropul` is a practical toolkit for meta-analysis in systematic reviews.
It provides a consistent workflow for ratio measures, continuous outcomes,
single proportions, subgroup analysis, meta-regression, influence diagnostics,
publication-bias assessment, risk-of-bias figures, and non-pooling umbrella
reviews.

## Installation

Install the development version from GitHub:

``` r
# install.packages("pak")
pak::pak("drrubesh/metapropul")
```

## Graphical interface

Users who prefer a point-and-click workflow can launch the optional Shiny
interface. It supports CSV and Excel upload, bundled examples, all six core analysis
families, subgroup analysis, model controls, forest plots, tables, diagnostics,
downloads, and an equivalent reproducible R call. A guided, numbered workflow
keeps every stage visible in sequence and includes controls to start over or
close the local application. Every analytical figure can be downloaded as PDF,
PNG, SVG, or TIFF, and every result table as Word, CSV, or PDF.
Publication-bias assessment can display one selected method or all four methods
in a 2-by-2 panel.

The Risk of bias workspace can also combine the current meta-analysis with an
uploaded ROB assessment in one aligned forest-and-traffic-light figure. Study
labels are checked before plotting to prevent judgements being assigned to the
wrong estimates.

See [Preparing CSV and Excel data](articles/input-data-formats.html) for the
required columns and scales for every analysis family. The GUI displays the
same context-sensitive guidance and provides a CSV template for the selected
input format. Subgroup analysis is never preselected: the GUI starts at
**None**, even when a bundled or uploaded dataset contains a subgroup column.

``` r
install.packages(c("shiny", "bslib", "readxl")) # once, if needed
metapropul::metapropul_app()
```

Plot titles remain blank unless the user enters one.

## Quick example

```{r example, message=FALSE}
library(metapropul)
data("dat_bcg", package = "metapropul")

dat_bcg$ncon <- dat_bcg$cpos + dat_bcg$cneg

fit <- meta_ratio(
  dat_bcg,
  event.e = "tpos", n.e = "npos",
  event.c = "cpos", n.c = "ncon",
  studylab = "author", subgroup = "alloc",
  measure = "OR", model = "random"
)

summary(fit)
```

Create publication-oriented outputs with the same fitted object:

```{r forest, eval=FALSE}
forest_meta(fit)
table_meta(fit)
plot_baujat(fit)
publication_bias(fit, plot_method = "original")
```

## Analysis families

- `meta_ratio()` analyses odds ratios, risk ratios, and pre-computed hazard ratios.
- `meta_mean()` analyses mean differences and standardised mean differences.
- `meta_prop()` analyses single proportions using logit or Freeman--Tukey transformations.
- `meta_generic()` pools estimates supplied with standard errors, variances, or
  confidence intervals.
- `meta_cor()` pools correlations using Fisher's z transformation.
- `meta_rate()` pools incidence rates from events and person-time.
- `meta_reg()` supports continuous and categorical moderators, interactions,
  Knapp--Hartung inference, predictions, and diagnostics.
- `umbrella_review()` organises reported review-level results without calculating
  a new pooled estimate across meta-analyses.

The package includes a getting-started vignette, worked case studies, and a
complete function reference. Run `browseVignettes("metapropul")` after
installation or use the Articles and Reference sections of the pkgdown site.
