---
title: "Case study: Tuberculosis proportions and meta-regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case study: Tuberculosis proportions and meta-regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 9,
  fig.height = 6, message = FALSE, warning = FALSE)
render_gt <- function(expr) {
  invisible(utils::capture.output(table <- force(expr)))
  cat(gt::as_raw_html(table))
}
```

This case study estimates tuberculosis event proportions in BCG study arms and
then investigates latitude as a moderator. It demonstrates single-proportion
transformations and the complete meta-regression workflow.

```{r}
library(metapropul)
data("dat_bcg", package = "metapropul")
```

## Proportion meta-analysis and subgroups

```{r}
prop_logit <- meta_prop(
  dat_bcg, event = "tpos", n = "npos",
  studylab = "author", subgroup = "alloc",
  sm = "PLOGIT", model = "random", ci_method = "HK"
)
summary(prop_logit)
prop_logit$meta.subgroup.summary
```

The Freeman--Tukey option is retained for compatibility, but its
back-transformation can be difficult to interpret and can behave poorly when
study sizes differ. It is shown below only as a sensitivity analysis; logit or
GLMM approaches are generally preferable for the primary analysis.

```{r}
prop_pft <- meta_prop(
  dat_bcg, "tpos", "npos", studylab = "author",
  subgroup = "alloc", sm = "PFT", model = "fixed"
)
summary(prop_pft)
```

```{r proportion-table, results='asis'}
render_gt(table_meta(prop_logit, title = "Tuberculosis events in BCG study arms"))
```

```{r proportion-forest, fig.height=8}
forest_meta(prop_logit)
```

## Univariable meta-regression

Latitude is centred so that the intercept refers to the effect at the mean
latitude. Knapp--Hartung inference is requested explicitly.

```{r}
reg_latitude <- meta_reg(
  prop_logit, dat_bcg, ~ ablat,
  studylab = "author", center = "ablat", test = "knha",
  min_studies_per_parameter = 3
)
summary(reg_latitude)
```

```{r regression-table, results='asis'}
render_gt(table_meta_reg(reg_latitude))
```

## Predicted proportions

```{r}
predict_meta_reg(
  reg_latitude,
  newdata = data.frame(ablat = c(10, 30, 50)),
  scale = "response"
)
```

## Bubble plot with confidence and prediction bands

```{r bubble}
plot_meta_reg(reg_latitude, type = "bubble", moderator = "ablat")
```

`bubble_plot()` is retained as a convenient wrapper around the same plotting
system.

```{r bubble-wrapper}
bubble_plot(reg_latitude, moderator = "ablat")
```

## Residual, fitted-value, and influence diagnostics

```{r}
reg_diagnostics <- diagnose_meta_reg(reg_latitude)
reg_diagnostics$collinearity
head(reg_diagnostics$studies)
```

```{r residual}
plot_meta_reg(reg_latitude, type = "residual")
```

```{r fitted}
plot_meta_reg(reg_latitude, type = "fitted")
```

```{r regression-influence}
plot_meta_reg(reg_latitude, type = "influence")
```

## Categorical moderators and interactions

The multivariable example fixes the categorical reference level, standardises
latitude, and includes an interaction. With only 13 studies, it is deliberately
illustrative and should not be treated as a well-powered substantive model.

```{r}
reg_interaction <- meta_reg(
  prop_logit, dat_bcg, ~ ablat * alloc,
  studylab = "author", reference_levels = c(alloc = "random"),
  scale = "ablat", min_studies_per_parameter = 2
)
summary(reg_interaction)
diagnose_meta_reg(reg_interaction)$collinearity
```
