---
title: "Case study: Continuous outcomes and study appraisal"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case study: Continuous outcomes and study appraisal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 9,
  fig.height = 6, message = FALSE, warning = FALSE)
render_gt <- function(expr) {
  invisible(utils::capture.output(table <- force(expr)))
  cat(gt::as_raw_html(table))
}
```

This case study demonstrates continuous-outcome meta-analysis and then uses a
second bundled dataset to show risk-of-bias visualisation.

```{r}
library(metapropul)
data("dat_normand1999", package = "metapropul")
dat_normand1999$period <- ifelse(
  seq_len(nrow(dat_normand1999)) <= 4, "Earlier", "Later"
)
```

## Mean difference and subgroup analysis

```{r}
mean_md <- meta_mean(
  dat_normand1999,
  mean.e = "m1i", sd.e = "sd1i", n.e = "n1i",
  mean.c = "m2i", sd.c = "sd2i", n.c = "n2i",
  studylab = "source", subgroup = "period",
  measure = "MD", model = "random", ci_method = "HK"
)
summary(mean_md)
mean_md$meta.subgroup.summary
```

A fixed-effect standardised mean difference provides a sensitivity analysis
on a common scale.

```{r}
mean_smd <- meta_mean(
  dat_normand1999, "m1i", "sd1i", "n1i", "m2i", "sd2i", "n2i",
  studylab = "source", subgroup = "period",
  measure = "SMD", model = "fixed"
)
summary(mean_smd)
```

```{r mean-table, results='asis'}
render_gt(table_meta(mean_md, title = "Continuous-outcome meta-analysis"))
```

```{r mean-forest, fig.height=7}
forest_meta(mean_md)
```

## Influence and cumulative analyses

```{r mean-influence-table, results='asis'}
render_gt(table_influence(mean_md))
```

```{r mean-influence-forest}
forest_influence(mean_md)
```

```{r mean-cumulative-table, results='asis'}
render_gt(table_cumulative_meta(mean_md))
```

```{r mean-cumulative-forest}
forest_cumulative(mean_md)
```

## Heterogeneity and DOI assessment

```{r mean-heterogeneity}
plot_heterogeneity(mean_md)
```

```{r mean-baujat}
plot_baujat(mean_md)
```

There are fewer than ten studies, so this example uses the DOI plot rather
than treating funnel-asymmetry tests as reliable.

```{r doi}
doi_plot(mean_md)
```

## Risk-of-bias figures

The bundled caffeine dataset contains five domain judgements and an overall
judgement. The labels are passed as a custom appraisal scheme so the example
uses exactly the levels present in the source data.

```{r}
data("caffeine", package = "metapropul")
domains <- c("D1", "D2", "D3", "D4", "D5", "rob")
judgements <- unique(unlist(caffeine[domains], use.names = FALSE))
judgements <- judgements[!is.na(judgements)]
```

```{r rob-traffic, fig.width=10, fig.height=6}
plot_rob(
  caffeine, "study", tool = "Custom",
  domains = domains, levels = judgements
)
```

```{r rob-summary}
plot_rob_summary(
  caffeine, "study", tool = "Custom",
  domains = domains, levels = judgements
)
```

Risk-of-bias judgements should inform interpretation and sensitivity analysis;
they are not statistical weights and should not be converted mechanically into
quality scores.
