---
title: "Case study: BCG vaccine effectiveness"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case study: BCG vaccine effectiveness}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 9,
  fig.height = 6, message = FALSE, warning = FALSE)
render_gt <- function(expr) {
  invisible(utils::capture.output(table <- force(expr)))
  cat(gt::as_raw_html(table))
}
```

This case study asks whether BCG vaccination reduces tuberculosis and whether
the effect differs by allocation method. It demonstrates the complete
two-group binary-outcome workflow.

```{r}
library(metapropul)
data("dat_bcg", package = "metapropul")
dat_bcg$ncon <- dat_bcg$cpos + dat_bcg$cneg
```

## Random-effects odds ratios and subgroups

```{r}
bcg_or <- meta_ratio(
  dat_bcg,
  event.e = "tpos", n.e = "npos",
  event.c = "cpos", n.c = "ncon",
  studylab = "author", subgroup = "alloc",
  measure = "OR", model = "random",
  tau_method = "REML", ci_method = "HK"
)
summary(bcg_or)
```

The subgroup rows are reported separately; the subgroup-difference test should
not be interpreted as proof that subgroups are equivalent when non-significant.

```{r}
bcg_or$meta.subgroup.summary
```

For comparison, a fixed-effect risk-ratio analysis uses the same raw data.

```{r}
bcg_rr_fixed <- meta_ratio(
  dat_bcg, "tpos", "npos", "cpos", "ncon",
  studylab = "author", subgroup = "alloc",
  measure = "RR", model = "fixed"
)
summary(bcg_rr_fixed)
```

## Main results and forest plot

```{r results-table, results='asis'}
render_gt(table_meta(bcg_or, title = "BCG vaccination and tuberculosis"))
```

```{r forest, fig.height=8}
forest_meta(bcg_or, title = "BCG vaccination by allocation method")
```

## Leave-one-out influence analysis

```{r influence-table, results='asis'}
render_gt(table_influence(bcg_or))
```

```{r influence-forest, fig.height=7}
forest_influence(bcg_or)
```

## Cumulative evidence

The cumulative analysis uses study order in the fitted object. In an applied
review, arrange the source data by publication year before fitting when a
chronological cumulative analysis is intended.

```{r cumulative-table, results='asis'}
render_gt(table_cumulative_meta(bcg_or))
```

```{r cumulative-forest, fig.height=7}
forest_cumulative(bcg_or)
```

## Heterogeneity and contribution

```{r heterogeneity}
plot_heterogeneity(bcg_or)
```

```{r baujat}
plot_baujat(bcg_or)
```

## Publication-bias assessment

Formal asymmetry statistics can be unavailable for some fitted models. The
function reports that limitation and still returns the supported diagnostics.

```{r publication-bias, fig.width=9, fig.height=7}
publication_bias(bcg_or, plot_method = "original")
```

The numerical results, influence patterns, heterogeneity, and possible
small-study effects should be interpreted together rather than using any
single diagnostic as a decision rule.
