---
title: "Case study: generic effects, correlations, and incidence rates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case study: generic effects, correlations, and incidence rates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 8,
                      fig.height = 5.5, dpi = 120)
library(metapropul)

render_gt <- function(expr) {
  table <- eval.parent(substitute(expr))
  cat(gt::as_raw_html(table))
}
```

This case study covers three common situations that do not use raw two-arm
means or binary-event counts: published estimates with standard errors,
correlations with sample sizes, and incidence rates based on person-time.

## Generic inverse-variance meta-analysis

`meta_generic()` pools study estimates when an effect and its uncertainty are
already available. `Pagliaro1992` contains log odds ratios and standard errors.
Some identifiers repeat, so `duplicate_action = "make_unique"` preserves every
row while creating unambiguous display labels.

```{r generic-model}
generic_fit <- meta_generic(
  Pagliaro1992, effect = "logOR", se = "selogOR", studylab = "id",
  measure = "Odds ratio", backtransform = "exp",
  duplicate_action = "make_unique"
)
summary(generic_fit)
```

```{r generic-table, results='asis'}
render_gt(table_meta(generic_fit))
```

```{r generic-forest, fig.cap="Generic inverse-variance meta-analysis of odds ratios."}
forest_meta(generic_fit)
```

The analysis is performed on the log scale and displayed on the odds-ratio
scale, avoiding invalid arithmetic while keeping the output interpretable.

## Meta-analysis of correlations

`meta_cor()` applies Fisher's z transformation internally and returns results
on the correlation scale. This small dataset is simulated solely to make the
workflow reproducible.

```{r correlation-data}
correlations <- data.frame(
  study = paste("Study", LETTERS[1:8]),
  r = c(0.12, 0.21, 0.35, 0.28, 0.44, 0.18, 0.39, 0.31),
  n = c(82, 115, 74, 160, 93, 126, 105, 141)
)
cor_fit <- meta_cor(correlations, cor = "r", n = "n",
                    studylab = "study")
summary(cor_fit)
```

```{r correlation-table, results='asis'}
render_gt(table_meta(cor_fit))
```

```{r correlation-forest, fig.cap="Meta-analysis displayed on the correlation scale."}
forest_meta(cor_fit)
```

Correlations must lie strictly between -1 and 1, and each study must have more
than three observations. The function checks these conditions before fitting.

## Meta-analysis of incidence rates

`meta_rate()` pools event rates while accounting for differing amounts of
person-time. `lungcancer` reports deaths and person-years among smokers. Rates
are displayed per 100,000 person-years.

```{r rate-model}
rate_fit <- meta_rate(
  lungcancer, event = "d.smokers", time = "py.smokers",
  studylab = "study", irscale = 100000, irunit = "person-years"
)
summary(rate_fit)
```

```{r rate-table, results='asis'}
render_gt(table_meta(rate_fit))
```

```{r rate-forest, fig.cap="Incidence-rate meta-analysis per 100,000 person-years."}
forest_meta(rate_fit)
```

Zero-event studies are retained using the requested continuity correction.
The original events and person-time remain in the fitted object's analysis data
for audit and reporting.

## Choosing a function

Use `meta_generic()` for an effect estimate with a standard error, variance, or
confidence interval; `meta_cor()` for correlations and sample sizes; and
`meta_rate()` for event counts with person-time. For raw binary, continuous, or
proportion data, use `meta_ratio()`, `meta_mean()`, or `meta_prop()` instead.
