---
title: "Preparing CSV and Excel data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preparing CSV and Excel data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`metapropul` expects one row per independent study or comparison. CSV and Excel
headers can use any names: function arguments and the graphical interface map
your headers to their statistical roles. Numeric analysis columns must contain
numbers rather than formatted strings such as `"12%"` or `"1,250"`.

The optional `study` column identifies studies and the optional `subgroup`
column identifies a completely observed subgroup. Merely having a subgroup
column in the file does not request subgroup analysis: `subgroup = NULL` is the
function default, and the GUI always starts at **None**. Select a subgroup only
when it is scientifically intended. Avoid duplicate study labels where
possible. The GUI shows the required headers for the selected analysis and
provides a downloadable CSV template.

## Ratio outcomes: OR, RR, and HR

Odds ratios and risk ratios can be calculated from a 2 by 2 table:

| study | event_e | n_e | event_c | n_c | subgroup |
|:--|--:|--:|--:|--:|:--|
| Study 1 | 12 | 100 | 20 | 100 | Europe |
| Study 2 | 8 | 80 | 15 | 75 | Asia |

```{r, eval=FALSE}
meta_ratio(dat, "event_e", "n_e", "event_c", "n_c",
  studylab = "study", subgroup = "subgroup", measure = "OR")
```

Reported OR, RR, or HR values can be supplied with confidence limits. These
three columns are on the ordinary ratio scale and must be positive:

| study | effect | lower | upper |
|:--|--:|--:|--:|
| Study 1 | 0.72 | 0.51 | 1.02 |
| Study 2 | 1.18 | 0.88 | 1.58 |

```{r, eval=FALSE}
meta_ratio(dat, effect = "effect", lower = "lower", upper = "upper",
  studylab = "study", measure = "HR")
```

Log OR, log RR, or log HR may instead be supplied with its standard error:

| study | log_effect | se |
|:--|--:|--:|
| Study 1 | -0.329 | 0.177 |
| Study 2 | 0.165 | 0.150 |

```{r, eval=FALSE}
meta_ratio(dat, effect = "log_effect", se = "se", effect_scale = "log",
  studylab = "study", measure = "HR")
```

Hazard ratios cannot be reconstructed from simple event totals; use one of the
two pre-computed formats. Do not enter a ratio as `effect` when
`effect_scale = "log"`.

## Continuous outcomes

Raw MD or SMD analysis requires both group summaries:

| study | mean_e | sd_e | n_e | mean_c | sd_c | n_c |
|:--|--:|--:|--:|--:|--:|--:|
| Study 1 | 12.1 | 3.2 | 60 | 14.0 | 3.5 | 58 |
| Study 2 | 10.8 | 2.9 | 45 | 12.2 | 3.1 | 47 |

Alternatively, use `effect`, `lower`, and `upper` for a reported MD or SMD.
Use `meta_generic()` for a continuous effect supplied with an SE or variance.

## Proportions

Provide event counts and total sample sizes. Each event count must lie between
zero and its corresponding total:

| study | event | n | subgroup |
|:--|--:|--:|:--|
| Study 1 | 18 | 200 | Hospital |
| Study 2 | 7 | 95 | Community |

## Generic inverse-variance effects

Provide `effect` plus exactly one of `se`, `variance`, or the pair `lower` and
`upper`. Effects stay on their analysis scale. For a log ratio and SE, choose
`backtransform = "exp"`; for an untransformed estimate choose `"identity"`.

## Correlations and incidence rates

Correlation analysis requires `cor` and `n`; correlations must be strictly
between -1 and 1 and `n` must exceed 3. Incidence-rate analysis requires
non-negative `event` and positive `person_time` columns.

## Risk-of-bias files

Use one row per study, one study-label column, and one column per ROB domain.
Labels must match the fitted meta-analysis exactly when creating a combined
forest and ROB figure. Judgements must use the levels of the selected tool, for
example `Low`, `Some concerns`, and `High` for a generic three-level tool.

## Meta-regression prediction files

Fit meta-regression using moderator columns in the primary study dataset. A
prediction file contains only the moderator combinations to estimate: its
headers and data types must match the moderators used in the model. Do not add
effect estimates or standard errors. The GUI creates a template from the
fitted model so categorical levels and numeric columns are preserved.

## Umbrella-review results

Use one row per reported meta-analysis result. Required columns are `outcome`,
`review`, `effect`, `lower`, and `upper`. Useful optional columns include
`measure`, `studies`, `participants`, `i2`, `p_value`, `year`, `quality`, and
`certainty`. Each row remains a separate reported synthesis; metapropul does
not pool rows across reviews.

## Primary-study overlap (CCA)

CCA input is long-format membership data:

| review | primary_study | outcome | included |
|:--|:--|:--|:--|
| Review A | Study 1 | Mortality | TRUE |
| Review A | Study 2 | Mortality | TRUE |
| Review B | Study 1 | Mortality | TRUE |

`review` and `primary_study` are required. `outcome` and `included` are
optional. An inclusion indicator may contain only `TRUE`/`FALSE`, `1`/`0`, or
`NA`; `NA` means that the review--study cell is structurally unavailable.

## Primary-study diagnostics within reviews

Use one row per primary-study estimate with `outcome`, `review`,
`primary_study`, `effect`, `lower`, and `upper`; participant count is optional.
Every outcome--review group needs at least two unique primary studies. These
data are diagnosed within each source review and are never pooled across
reviews.
