---
title: "Umbrella reviews without pooling meta-analyses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Umbrella reviews without pooling meta-analyses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
render_gt <- function(expr) {
  invisible(utils::capture.output(table <- force(expr)))
  cat(gt::as_raw_html(table))
}
```

The umbrella-review functions preserve each published meta-analysis as a
separate result. They do not combine reviews into a new pooled estimate.

```{r}
library(metapropul)

reviews <- data.frame(
  outcome = rep(c("Cardiovascular disease", "Mortality"), each = 2),
  review = c("Review A", "Review B", "Review C", "Review D"),
  estimate = c(0.78, 0.83, 1.12, 1.06),
  lower = c(0.70, 0.75, 1.02, 0.97),
  upper = c(0.87, 0.92, 1.23, 1.16),
  studies = c(14, 11, 8, 12),
  participants = c(3000, 2500, 1800, 2200),
  i2 = c(20, 45, 55, 40),
  p = c(1e-7, 2e-5, 0.01, 0.12),
  pred_lower = c(0.71, 0.69, 0.98, 0.94),
  pred_upper = c(0.88, 0.98, 1.28, 1.20),
  year = c(2022, 2024, 2020, 2025),
  quality = c("High", "Moderate", "Low", "High"),
  risk = c("Low", "Some concerns", "High", "Low")
)

umbrella <- umbrella_review(
  reviews, "outcome", "review", "estimate", "lower", "upper",
  studies = "studies", participants = "participants", i2 = "i2",
  p_value = "p", pred_lower = "pred_lower", pred_upper = "pred_upper",
  year = "year", quality = "quality",
  risk_of_bias = "risk"
)
umbrella
```

## Credibility, GRADE, and review quality

These are intentionally distinct assessments:

```{r}
credibility <- classify_umbrella(umbrella)
grade <- grade_umbrella(
  umbrella, starting_certainty = "high",
  risk_of_bias = c("not_serious", "serious", "very_serious", "not_serious")
)
quality <- assess_review_quality(umbrella, tool = "AMSTAR2", overall = "quality")

credibility[, c("Outcome", "Review", "EvidenceClass")]
grade[, c("Outcome", "Review", "GRADE")]
quality
```

`classify_umbrella()` applies quantitative credibility rules. `grade_umbrella()`
records reviewer-supplied GRADE judgements; it does not infer GRADE domains from
statistical results. `assess_review_quality()` records AMSTAR 2 or ROBIS results.

```{r umbrella-table, results='asis'}
render_gt(table_umbrella(umbrella, credibility, grade))
```

```{r umbrella-plot, fig.width=9, fig.height=5.5}
plot_umbrella(umbrella, credibility)
```

The plot contains one interval per reported meta-analysis and deliberately has
no pooled diamond.

## Diagnostics from primary studies

When primary-study estimates have been extracted, diagnostics are calculated
separately inside each source review. The example data below are deterministic
teaching values rather than a reconstruction of a published review.

```{r}
primary <- do.call(rbind, lapply(seq_len(nrow(reviews)), function(i) {
  se <- seq(0.10, 0.16, length.out = 5)
  centre <- log(reviews$estimate[i])
  yi <- centre + c(-0.08, -0.03, 0, 0.04, 0.09)
  data.frame(
    outcome = reviews$outcome[i], review = reviews$review[i],
    study = paste0(reviews$review[i], "-S", seq_along(se)),
    effect = exp(yi), lower = exp(yi - 1.96 * se),
    upper = exp(yi + 1.96 * se),
    participants = seq(400, 1200, length.out = 5)
  )
}))

primary_diagnostics <- diagnose_umbrella_primary(
  primary, "outcome", "review", "study", "effect", "lower", "upper",
  participants = "participants", min_egger = 3
)
primary_diagnostics$summary
classify_umbrella(umbrella, primary_diagnostics)[,
  c("Outcome", "Review", "EvidenceClass")]
```

## Primary-study overlap

```{r}
membership <- data.frame(
  outcome = rep("Cardiovascular disease", 8),
  review = rep(c("Review A", "Review B"), each = 4),
  study = c("S1", "S2", "S3", "S4", "S2", "S3", "S4", "S5")
)

overlap <- study_overlap(membership, "review", "study", "outcome")
overlap$overall
overlap$pairwise
```

`plot_study_overlap()` displays the citation matrix, pairwise Jaccard overlap,
or corrected covered area. `sensitivity_umbrella_overlap()` compares which
reported review would be retained under prespecified selection strategies; it
does not pool the selected reviews.

```{r overlap-plot, fig.width=7, fig.height=4.5}
plot_study_overlap(overlap, type = "citation_matrix")
```

```{r jaccard-plot, fig.width=7, fig.height=4.5}
plot_study_overlap(overlap, type = "jaccard")
```

```{r cca-plot, fig.width=7, fig.height=4.5}
plot_study_overlap(overlap, type = "cca")
```

The triangular CCA heatmap follows the convention used by `ccaR`: pairwise CCA
percentages appear below the diagonal, while grey diagonal cells show the
number of unique primary studies in each review. For several outcomes, an
overall summary bar plot is also available.

```{r cca-summary-plot, fig.width=7, fig.height=4.5}
plot_study_overlap(overlap, type = "cca_summary")
```

## Review-selection sensitivity

Selection strategies choose one already reported result per outcome; they do
not calculate a synthesis across reviews.

```{r}
sensitivity_umbrella_overlap(
  umbrella, overlap,
  strategies = c(
    "highest_quality", "lowest_risk_of_bias", "most_recent",
    "most_comprehensive", "largest_participant_count", "lowest_overlap",
    "user_selected"
  ),
  user_selected = c(
    "Cardiovascular disease" = "Review B",
    "Mortality" = "Review D"
  )
)[, c("Outcome", "Review", "Strategy", "Estimate")]
```
